---
title: "rename"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = '.')
```


```{r}
library(pmtables)
vars <- dplyr::vars
```

# Motivation

I wanted a way to capture column names as a character vector along with a 
second set of names for renaming those data items. The primary need was
a vector of names to use rather columns to select from a data set. 

# Solution

`new_names` class with methods for character and quosure.  This is two methods
and the generic.

```{r}
pmtables:::new_names("a,b,c")
```

```{r}
pmtables:::new_names(c("a", "b", "c"))
```

```{r}
pmtables:::new_names(vars(a,b,c))
```
```{r}
pmtables:::new_names(vars(A = a, B = b, C = c))
```


# Also accepts rename as named list

- new names cal also be added through a named list
- this is the third function 

```{r}
re <- list(A = "a", B = "b")

pmtables:::new_names("A,B", table = re)

```

This is a little backward from the `rename(new_name = old_name)` syntax; but 
it is made to handle output from yspec, where things are already keyed by the 
existing column name. This could easily be modified to invert names / values
during this lookup process.


## Works with select

- My main movitation was to get a character vector along with re-names in a 
convenient and flexible way. The output can also be used to drive tidyverse
select and rename functionality:

```{r, message=FALSE}
library(dplyr)
x <- pmtables:::new_names(vars(b = B, a = A))

x

tab <- tibble(A = 1, B = 2)


tab

select(tab,all_of(x))
```

## Or rename

```{r}
rename(tab, all_of(x))
```

