---
title: "Continuous Data Table"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
%\VignetteIndexEntry{Continuous Data Table}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  ---
  
  ```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "."
)
```


These functions create summary tables for continuous data. There is a long 
format and a wide format.


# Long format

```{r, message = FALSE, warning = FALSE}
library(pmtables)
library(dplyr)

id <- pmtables:::data("id") 
```

A summary of covariates 

```{r}
pt_cont_long(id, cols = "WT,ALB,SCR")
```

# Paneled summary

Use the panel argument to split this by, for example, study 

```{r}
pt_cont_long(
  id, 
  cols = "WT,ALB,SCR",
  panel = vars(Study = STUDYf)
)
```




# Wide format

There is also a wide format, where variable names go across the table.

```{r}
pt_cont_wide(id, cols = "WT,ALB,SCR")
```

We can use the by argument here
```{r}
pt_cont_wide(id,cols="WT,ALB,SCR",by = vars(Study = STUDYf))
```



Or use by and panel

```{r}
pt_cont_wide(
  id,
  cols=vars(WT,ALB,SCR),
  by = vars(Study = STUDYf),
  panel=vars(Sex = SEXf)
)
```


