---
title: "Custom Digits"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Custom Digits}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "."
)
```


For continuous data summaries, the number of digits can be 
controlled by setting the `digits` option with a `digits` object.

# Digits objects

Create a new digits object

```{r}
library(pmtables)

x <- new_digits()
x
```

By default, pmtables will format numeric summaries with 3 
significant digits. 


## Select number of digits by default

To use a default of 2 significant digits

```{r}
x <- new_digits(.default = 2)
x
```


To customize the number of digits for each data summary

```{r}
x <- new_digits(WT = 3, ALB = 4, SCR = 2)

x
```

This will use 3 significant digits for `WT`, 4 for `ALB` and 
2 for `SCR`.


## Select the function to use for digits

We can also round digits. It is safest to create your own wrapper
for round instead of using `round` (a primitive function)

```{r}
x <- new_digits(.fun = round)
x
```


# Using custom digits

Use the `digits` option

This should give us 2 digits in all columns except for `WT`, 
which should be 3 digits

```{r}
dig <- new_digits(.default = 2, WT = 3)
dig
```

```{r}
pt_opts$set(digits = dig)
```

```{r}
data <- pmtables:::data("id")
```

```{r}
pt_cont_long(
  data, 
  cols = "WT,ALB,SCR,CRCL"
)
```




