---
title: "(re)naming columns in your table"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{(re)naming columns in your table}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "."
)
```

We can re-name the various column names in the output table


# Rename via list

We make a named list with re-names for each column we are summarizing or 
paneling by.
```{r}
table <- list(WT = "weight", BMI = "body mass index", SCR = "serum creatinine")
```

Here we created the list manually; you can also pull this information 
out of the data specification object.

## Example

We pass this table list into the continuous covariate table function

```{r, message = FALSE, warning = FALSE}
library(pmtables)
library(dplyr)

data <- pmtables:::data("id")

pt_cont_long(
  data, 
  cols = "BMI,SCR,WT", 
  table = table
)
```



# Rename inline

Rather than creating that list of renames, we can re-name in line using the 
vars constructor


```{r}
pt_cat_wide(
  data, 
  cols = vars(Sex = SEXf, Formaulation = FORMf), 
  by = vars("Study ID" = STUDYf)
)
```


We can also rename the `panel` or `by` variable

```{r}
obs <- pmtables:::data("obs")

pt_data_inventory(
  obs, 
  by = vars(Sex = SEXf), 
  panel = vars(Formulation = FORMf)
)
  
```


## Use R to rename factor levels

Remember, you are on the hook to label or relabel your factors

```{r}
data2 <- mutate( data, SEXf = factor(SEXf, labels = c("dude", "gal")))

pt_cat_wide(
  data2, 
  cols = vars(Sex = SEXf, Formulation = FORMf), 
  by = vars("Study ID" = STUDYf)
)
```

