---
title: "Data Inventory Table"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Inventory Table}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "."
)
```


The data inventory table counts subjects and observations in your data set. 
It will also tally missing or BQL observations.


# Basic table by study

```{r, message = FALSE, warning = FALSE}
library(pmtables)
library(dplyr)

all <- pmtables:::data("obs") 
pk <- filter(all, SEQ==1)
```

A summary of PK data by study
```{r}
pt_data_inventory(pk, by = vars(Study = STUDYf))
```

# Paneled summary

We can also panel this summary by another covariate

```{r}
pt_data_inventory(
  pk, 
  by = vars(Study = STUDYf), 
  panel = vars("Renal function" = RFf)
)
```




# Stacked summary

Use this when you want to have a single table that summarizes different 
endpoints. This is a paneled summary where each panel is a summary only 
of what is in that panel.

```{r}
pt_data_inventory(
  all, 
  panel = vars(Endpoint = SEQf), 
  by = vars("Study" = STUDYf), 
  stacked = TRUE
)
```





