---
title: "pmtables"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pmtables}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---
  
```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "."
)
```

pmtables is a package for R that automates the building and formatting of some
tables that we commonly create when reporting modeling and simulation results
in pharmacometrics. 


# Tables

pmtable currently supports three main types of tables

1. continuous covariate summary (see [continuous-table.html]())
1. categorical / discrete covariate summary (see [discrete-table.html]())
1. data set inventory summary (number of observations, number of individuals, 
   etc) (see [data-inventory.html]())
   
pmtables receives your data set along with some options, summarizes the data in 
a very specific way and creates a very specifically formatted table. In this 
sense, pmtables is like pmplots: it is not a general grammar of tables 
(replacing gt or mrggt or kable etc) but the goal is to make a very specific 
table. We designed pmtables to make some very common tables in a very standard
way. If pmtables won't / can't make the table that you want, then the user 
should use tidyverse + mrggt to create a custom data summary and formatted
table.


# Vocabulary

## `cols` / `by`

For most tables, you will specify column names in two of four groups:

* `cols` is a character vector (or quosure) naming columns in the data set that 
  you would like summarized
* `by` is one grouping variable for the summary; `by` should be just a single 
  value
* `panel` is another grouping variable for the summary in a long format
* `span` identifies stratification variable for discrete data in long 
  format (see below)

## `wide` / `long`

You will also see that some tables are "wide" and some are "long": wide 
indicates that the summarized covariates / values run across the table 
(west to east) and long indicates that the covariates run along the left hand
side of the table (north to south).


### Example - wide

```{r,echo=FALSE}
data <- pmtables:::data("id")
```

```{r,message=FALSE,warning =FALSE}
library(pmtables)
library(dplyr)
```


For example, we can use `cols` and `by` to create a summary of continuous 
covariates (weight, serum creatinine, and albumin) by study ID in wide 
format:

```{r}
pt_cont_wide(
  data, 
  cols = vars(WT,SCR,ALB), 
  by = vars("Study ID" = STUDYf)
)
```


There is also a discrete data table in wide format

```{r}
pt_cat_wide(
  data, 
  cols = vars(Sex = SEXf, Formulation = FORMf), 
  by = vars("Study ID" = STUDYf)
)
```




## Example - long

We can also make these tables in long format. In the long format, the `by` 
option is used up by the variable names; but you can use the `panel` option 
to group a continuous summary and the `span` option to group a categorical
summary

The continuous summary would be:

```{r}
pt_cont_long(
  data, 
  cols = vars(WT,SCR,ALB), 
  panel = vars("Study ID" = STUDYf)
)
```

and the catetgorical summary would be:

```{r}
pt_cat_long(
  data, 
  cols = vars(Sex = SEXf, Formulation = FORMf), 
  span = vars("Study ID" = STUDYf)
)
```





   
   














