--- 
title: Simple Tables Demo Doc
output: 
  pdf_document: 
    extra_dependencies: 
      threeparttable:
      booktabs:
      longtable:
      mathdesign: utopia
      array:
    number_sections: true
    toc: true 
editor_options: 
  chunk_output_type: inline
---

```{r,message = FALSE, echo=FALSE}
library(dplyr)
library(purrr)
```

\clearpage

# Data

Mostly working with this data; but some others come in later to illustrate
certain features.

```{r}
library(pmtables)
library(yspec)
spec <- ys_help$spec()

data <- pmt_summarized

data
```


# wrap

There is a wrap function in this document.  Don't worry about that; it just 
puts the output into a table environment and sends the output to get rendered
in markdown.

\clearpage

# Simple table

- Columns are in bold by default (can be turned off)

```{r,results = 'asis'}
data %>% stable() %>% pt_wrap(stdout())
```
\clearpage


# Long table

```{r}
data <- ptdata()
data <- map_dfr(1:2, ~ data) %>% arrange(STUDY,DOSE,FORM)
```


```{r,results = "asis"}
data %>%
  stable_long(
    panel = "STUDY", col_bold = TRUE,
    units = ys_get_unit(spec, parens = TRUE),
    notes = "The results look great!",
    clear_reps = "DOSE",
    col_rename = c(Formulation  = "FORM"),
    r_file = "foo.R", output_file = "../deliv/table/output.tex",
    note_config = noteconf(type = "minipage", width = 0.8,table_skip = 0.2)
  ) %>% as.character() %>% writeLines
```


\clearpage

# Annotate

- Arguments to identify the name of the generating R script and the output file
  name
- The output file name is retained as an attribute to be used later when saving
  the table data
- Arbitrary notes are also allowed (encouraged)

```{r,results = 'asis'}
stable(
  data[1:10,],
  r_file = "foo.R",
  output_file = "foo.tex",
  notes = c("Data were analyzed in quadruplicate.", "The results are very clear."),
) %>% pt_wrap(stdout())
```

