--- 
title: Simple Tables Demo Doc
output: 
  pdf_document: 
    extra_dependencies: 
      threeparttable:
      booktabs:
      longtable:
      mathdesign: utopia
      array:
    number_sections: true
    toc: true 
editor_options: 
  chunk_output_type: inline
---

```{r,message = FALSE, echo=FALSE}
library(dplyr)
library(purrr)
```

\clearpage

# Data

Mostly working with this data; but some others come in later to illustrate
certain features.

```{r}
library(pmtables)
library(yspec)
spec <- ys_help$spec()

data <- pmt_summarized

head(data)
```


# wrap

There is a wrap function in this document.  Don't worry about that; it just 
puts the output into a table environment and sends the output to get rendered
in markdown.

\clearpage

# Simple table

- A data frame is wrapped in tabular environment
- The table is created with threeparttable


```{r,results = 'asis'}
data %>% stable(cols_bold=TRUE) %>% pt_wrap(stdout())
```

\clearpage

# Annotate 

- Arguments to identify the name of the generating R script and the output file
  name
- The output file name is retained as an attribute to be used later when saving
  the table data
- Arbitrary notes are also allowed, provided as a character vector; item in the 
vector is placed on its own line

```{r,results = 'asis'}
stable(
  data, 
  r_file = "foo.R", 
  output_file = "foo.tex", 
  notes = c("Data were analyzed in quadruplicate.", "The results are very clear."),
) %>% pt_wrap(stdout())
```

\clearpage

# Notes in minipage

- By default, notes are put in the 3rd part of threeparttable
- Alternatively, we can put them in a minipage just below the table
- The width of the minipage needs to be set by the user

```{r,results = 'asis'}
stable(
  data, 
  note_config = noteconf(type = "minipage", width = 0.85),
  notes = c("Data were analyzed in quadruplicate.", "The results are very clear."),
) %>% pt_wrap(stdout())
```



\clearpage

# Align

- Columns can be aligned center, left or right
- Columns can be aligned with a fixed with and aligned left, center or right
- Helper functions are provided as `cols_center()`, `cols_left()`, `cols_right()`
- The syntax is to state the default / base alignment for all columns and then
pass exceptions to that default setting

- Center everything except for
  - `STUDY` (left)
  - `DOSE` and `SCR` (right)

```{r,results = 'asis'}
data %>% 
  stable(align = cols_center(STUDY = 'l', .r = "DOSE,SCR")) %>%
  pt_wrap(stdout())
```


\clearpage


# Units

- Automatically put units under the column name
- Units are supplied as a named list, where names correspond with the column name
prior to renaming
- The list can contain a subset of columns and can also contain names that are 
not in the table (there is no warning or error for the latter)

```{r,results = 'asis'}
units <- ys_get_unit(spec, parens = TRUE)

stable(
  data,
  units = units,
) %>% pt_wrap(stdout())
```
\clearpage

# Expand header rows

- Multiline table header 
- Unlimited number
- Use `...` to break
- Units go on the bottom row when they are supplied
- Items are always pushed to the bottom

```{r, results = 'asis'}
stable(
  data, 
  cols_rename = vars("Study...Number" = STUDY, "Serum...Albumin" = ALB), 
  units = units
) %>% pt_wrap(stdout())
```

\clearpage

# Math

- Columns with at least two `$` are "math" and will not be sanitized
- Otherwise the are functions to "prime" the data frame
  - The default is to convert every column to character
  - Then walk the columns, look for non-math columns and sanitize them

```{r}
ptab <- readRDS("datasets/ptab.RDS")
ptab
```


```{r, results = 'asis'}
stable(
  ptab, 
  align = cols_center(Parameter =  col_ragged(3), .l = "Symbol"), 
  panel = ".type"
  ) %>% pt_wrap(stdout())
```



\clearpage

# hline from column

- Use the column to determine where the hline should go

```{r,results = 'asis'}
stable(
  data,
  hline_from = "STUDY",
) %>% pt_wrap(stdout())
```

\clearpage


# hline anywhere

- Give row numbers for hline as logical or integer vector

```{r,results = 'asis'}
stable(
  data,
  hline_at = c(3,nrow(data))-1,
) %>% pt_wrap(stdout())
```


\clearpage

# Remove duplicate values

- Discard repeating values in a column
- Also `clear_grouped_reps` which recursively groups by the column names supplied
and clears the most distant column name in the groups

```{r,results = 'asis'}
stable(
  data,
  clear_reps = "STUDY",
) %>% pt_wrap(stdout())
```

\clearpage

# Add styling to data frame

- `tex_bold` will make table cells bold when they match `pattern`
- `tex_it` will make table cells italics when they match `pattern`
- styling is only added when there is at least one character
- input must be string
- combine this with `clear_rep` and `hline_from` to partition the table
```{r}
tmp <- ptdata()

tmp <- mutate(tmp, STUDY = tex_bold(as.character(STUDY)))
```

```{r,results = "asis"}
stable(
  tmp, 
  clear_reps = "STUDY", 
  hline_from = "STUDY", 
) %>% pt_wrap(stdout())
```

\clearpage

# Panel

- Divide the table using column contents
- The panel column data is split in non-repeating chunks
- An error is generated if there are multiple panels with the same name; this 
can be overridden
- A prefix can be supplied that gets pasted on the front of the column title; 
the prefix can also come from the name of the supplied panel panel ID
(e.g. `c(prefix_text = panel_name)`)

```{r,results = 'asis'}
stable(
  data,
  panel = as.panel("STUDY", prefix = "Study number: "),
) %>% pt_wrap(stdout())
```

\clearpage

# Drop column

- name columns that can be dropped from the table

```{r, results = 'asis'}
stable(data[1:3,], drop = "STUDY,FORM,DOSE") %>% pt_wrap(stdout())
```

- this works when there is a panel

```{r, results = 'asis'}
stable(data[1:3,], drop = "SCR,FORM,DOSE", panel = "STUDY") %>% pt_wrap(stdout())
```

\clearpage

# Colspan

- Group columns with a spaning line and a title
- The span goes above the highest row in the column header box

```{r,results = 'asis'}
stable(
  data,
  span = colgroup("In final model", WT:CRCL),
) %>% pt_wrap(stdout())
```


\clearpage

# Colspan - multiple

- Multiple groupings
- Multiple levels

```{r,results = 'asis'}

stable(
  data,
  span = list(
    colgroup("Meh", DOSE:WT),
    colgroup("Hrm", AGE:CRCL), 
    colgroup("Huh", ALB:SCR), 
    colgroup("Expert opinion", CRCL:SCR, level = 2)
  )
) %>% pt_wrap(stdout())
```


\clearpage

# Colspan - from cols

- We have some columns of the form `tag.name`
- These are split on the `sep` argument; the `tag` (common across columns in the 
group) forms the spanner title
- The column names are formed by splitting `tag.` off of `tag.name`

```{r}
dotdata <- readRDS("datasets/with-dots.RDS")
head(dotdata, n=2)
```

```{r,results = 'asis'}
stable(
  dotdata,
  span_split = colsplit(sep = '.'),
) %>% pt_wrap(stdout())
```

\clearpage

# Handle wide columns

- This shows using `col_ragged()` alignment to fix the width of a column that has
a lot of text in it


## `descr is` taking over the table
```{r,results = "asis"}
ptable <- readRDS("datasets/ptable.RDS")

stable(ptable) %>% pt_wrap(stdout())
```


## Limit `descr` to 5 cm

```{r, results = "asis"}
stable(
  ptable, 
  align = cols_center(descr = col_ragged(5))
) %>% pt_wrap(stdout())
```


\clearpage

# Identify a summary row

- We can point to one or more rows and style it up as a "summary row"
- The summary row can be styled 
  - with a horizontal line above
  - with bold text in a designated column
  - with alternate text in a designated column
- Multiple summary rows can be specified in a list

```{r}
df.total <- readRDS(file = "datasets/with-total.RDS")
df.total
```


```{r, results = "asis"}
stable(
  df.total, 
  sumrows = sumrow(
    df.total$STUDY == "all", 
    label = "All Studies", 
    bold = TRUE
  )
) %>% pt_wrap(stdout())
```


\clearpage

# Save the table to file 

- There is a output file attribute on the text that is returned
- When the `stable` output is passed to `stable_save()`, the attribute is used
as the output file name

```{r}
tab <- stable(data, output_file = "foo.tex")
str(tab)
```

This can be used to save 

```{r}
stable_save(tab)

file.exists("foo.tex")
```

\clearpage

# Long table

- Long table is based on a call to `stable`
- The table header, tabular environemnt and table notes are reused

```{r}
long <- ptdata()
long <- map_dfr(1:2, ~ long) %>% arrange(STUDY,DOSE,FORM)
```


```{r,results = "asis"}
long %>%
  stable_long(
    panel = "STUDY", cols_bold = TRUE,
    units = ys_get_unit(spec, parens = TRUE),
    notes = "The results look great!",
    clear_reps = "DOSE",
    cols_rename = c(Formulation  = "FORM"),
    r_file = "foo.R", output_file = "../deliv/table/output.tex",
    note_config = noteconf(type = "minipage", width = 0.8,table_skip = 0.2)
  ) %>% as.character() %>% writeLines
```



\clearpage


# Fontsize

- Tables should be rendered with `\\normalsize` for the most part
- The font size can get bumped up or down in special circumstances

```{r,results = 'asis'}
data %>% stable(sizes = tab_size(font = "tiny")) %>% pt_wrap(stdout())
```


\clearpage

# Row space

- The default rowspacing is 1.4; this is a multiplication factor
- The user can bring this up or down so that row spacing of 1 is no extension
or compression of row padding

```{r,results = 'asis'}
data %>% slice(1:3) %>% stable() %>% pt_wrap(stdout())
data %>% slice(1:3) %>% stable(sizes = tab_size(row = 0.9)) %>% pt_wrap(stdout())
data %>% slice(1:3) %>% stable(sizes = tab_size(row = 2))   %>% pt_wrap(stdout())
```
\clearpage

# Col space

- The default is 5

```{r,results = 'asis'}
data %>% stable(sizes = tab_size(col = 20)) %>% pt_wrap(stdout())
```

\clearpage

# Still ok

```{r, results = 'asis'}
stable(data) %>% pt_wrap(stdout())
```

