--- 
title: Simple Tables Demo Doc
output: 
  pdf_document: 
    extra_dependencies: 
      threeparttable:
      booktabs:
      longtable:
      mathdesign: utopia
      array:
      fontenc: T1
      setspace:
    number_sections: true
    toc: true 
editor_options: 
  chunk_output_type: inline
---

```{r,message = FALSE, echo=FALSE}
library(dplyr)
library(purrr)
```

\clearpage

# Data

Mostly working with this data; but some others come in later to illustrate
certain features.

```{r}
library(pmtables)
library(yspec)
spec <- ys_help$spec()

data <- pmt_summarized

data
```


# wrap

There is a wrap function in this document.  Don't worry about that; it just 
puts the output into a table environment and sends the output to get rendered
in markdown.

\clearpage

# Simple table

```{r}
data %>% stable(units = ys_get_unit(spec, parens = TRUE)) %>% st_asis()
```
\clearpage


# Long table

```{r}
data <- ptdata()
data <- map_dfr(1:3, ~ data) %>% arrange(STUDY,DOSE,FORM)
```


```{r}
data %>%
  stable_long(
    panel = "STUDY", cols_bold = TRUE,
    units = ys_get_unit(spec, parens = TRUE),
    notes = "The results look great!",
    clear_reps = "DOSE",
    cols_rename = c(Formulation  = "FORM"),
    r_file = "foo.R", output_file = "../deliv/table/output.tex",
    note_config = noteconf(type = "minipage", width = 0.8,table_skip = 0.1)
  ) %>% st_asis()
```

\clearpage

# Pass in the caption

```{r}
data %>%
  stable_long(
    panel = "STUDY", 
    cols_bold = TRUE,
    notes = "The results look great!",
    clear_reps = "DOSE",
    lt_cap_text  = "This is a super-interesting table.", 
    note_config = noteconf(type = "minipage", table_skip = 0.1)
  ) %>% st_asis()
```


\clearpage


# Use a caption from tex macro


- Write this into your tex document
```{text, eval=FALSE}
\newcommand{\myfbtable}{This is a caption from a macro}\vskip 0.5cm
```


- Then create the table with:

```{=latex}
\newcommand{\myfbtable}{This is a caption from a macro}\vskip 0.5cm
```


```{r}
data %>%
  stable_long(
    panel = "STUDY", 
    cols_bold = TRUE,
    notes = "FORM: formulation",
    r_file = "demo-longtable.Rmd", 
    output_file = "foo.tex",
    clear_reps = "DOSE",
    lt_cap_macro  = "myfbtable", 
    note_config = noteconf(width = 0.7, type = "minipage", table_skip = 0.1)
  ) %>% st_asis()
```


\clearpage

# Pass in the caption with short 

```{r}
data %>%
  stable_long(
    panel = "STUDY", 
    cols_bold = TRUE,
    notes = "The results look great!",
    clear_reps = "DOSE",
    lt_cap_short = "a table",
    lt_cap_text  = "This is a super-interesting table.", 
    note_config = noteconf(type = "minipage", table_skip = 0.1)
  ) %>% st_asis()
```

\clearpage

# Reduce row space

```{r}
data %>%
  stable_long(
    panel = "STUDY", 
    cols_bold = TRUE,
    notes = "FORM: formulation",
    r_file = "demo-longtable.Rmd", 
    output_file = "foo.tex",
    clear_reps = "DOSE",
    sizes = tab_size(row = 1),
    note_config = noteconf(width = 0.7, type = "minipage", table_skip = 0.1)
  ) %>% st_asis()
```

\clearpage

# Extra spance
```{r}
data %>%
  stable_long(
    panel = "STUDY", 
    cols_bold = TRUE,
    notes = "FORM: formulation",
    r_file = "demo-longtable.Rmd", 
    output_file = "foo.tex",
    clear_reps = "DOSE",
    sizes = tab_size(lt_row = 2),
    note_config = noteconf(width = 0.7, type = "minipage", table_skip = 0.1)
  ) %>% st_asis()
```

\clearpage
```{r}
data %>%
  stable_long(
    panel = "STUDY", 
    cols_bold = TRUE,
    notes = "FORM: formulation",
    r_file = "demo-longtable.Rmd", 
    output_file = "foo.tex",
    clear_reps = "DOSE",
    note_config = noteconf(width = 0.7, type = "minipage", table_skip = 0.1)
  ) %>% st_asis()
```

\clearpage

# Increase col space

```{r}
data %>%
  stable_long(
    panel = "STUDY", 
    cols_bold = TRUE,
    notes = "FORM: formulation",
    r_file = "demo-longtable.Rmd", 
    output_file = "foo.tex",
    clear_reps = "DOSE",
    sizes = tab_size(row = 1, col = 1),
    note_config = noteconf(width = 0.7, type = "minipage", table_skip = 0.1)
  ) %>% st_asis()
```


\clearpage

# Annotate

- Arguments to identify the name of the generating R script and the output file
  name
- The output file name is retained as an attribute to be used later when saving
  the table data
- Arbitrary notes are also allowed (encouraged)

```{r}
stable(
  data[1:10,],
  r_file = "foo.R",
  output_file = "foo.tex",
  notes = c("Data were analyzed in quadruplicate.", "The results are very clear."),
) %>% st_asis()
```

