--- 
title: Demo Doc - pipe interface
output: 
  pdf_document: 
    extra_dependencies: 
      mathdesign: utopia
    number_sections: true
    toc: true 
editor_options: 
  chunk_output_type: inline
---

```{r,message = FALSE, echo=FALSE}
library(dplyr)
```

\clearpage

# Data

Mostly working with this data; but some others come in later to illustrate
certain features.

```{r}
library(pmtables)
library(yspec)
library(dplyr)
spec <- ys_help$spec()

data <- pmt_summarized
head(data)
```

\clearpage

# Simple table


```{r}
data %>% st_new() %>% stable(cols_bold = TRUE) %>% st_asis()
```

\clearpage

# Annotate

- Arguments to identify the name of the generating R script and the output file
name
- The output file name is retained as an attribute to be used later when saving
the table data
- Arbitrary notes are also allowed (encouraged)

```{r}
data %>% 
  st_data() %>%
  st_files(r = "foo.R", output = "foo.tex") %>%
  st_notes(
    "Data were analyzed in quadruplicate.", 
    "The results are very clear."
  ) %>% stable() %>% st_asis()
```

\clearpage

# Notes in minipage

- By default, notes are put in the 3rd part of threeparttable
- Alternatively, we can put them in a minipage just below the table

```{r}
data %>% 
  st_new() %>% 
  st_files("foo.R", "foo.tex") %>% 
  st_noteconf(type = "minipage", width = 0.85) %>%
  st_notes(
    "Data were analyzed in quadruplicate.", 
    "The results are very clear."
  ) %>% stable() %>% st_asis()

```

\clearpage

# Align

- Center everything except for
- `STUDY` (left)
- `DOSE` and `SCR` (right)

```{r}
data %>% 
  st_new() %>% 
  st_align("c", STUDY = 'l', .r = "DOSE,SCR") %>% 
  stable() %>% st_asis()
```


\clearpage


# Units

- Automatically put units under the column name

```{r}

data %>% 
  st_new() %>% 
  st_center(STUDY = 'l', .r = "DOSE,SCR") %>% 
  st_units(WT = "kg", SCR = "mg/dL", DOSE = "mg") %>%
  stable() %>% st_asis()
```

Alternatively
```{r}
units <- ys_get_unit(spec, parens = TRUE)

data[1:3,] %>% 
  st_new() %>% 
  st_center(STUDY = 'l', .r = "DOSE,SCR") %>% 
  st_units(units) %>%
  stable() %>% st_asis()
```

\clearpage

# Expand header rows

- Multiline table header 
- Unlimited number
- Use `...` to break

```{r}
data %>% 
  st_new() %>% 
  st_rename("Study...Number" = STUDY, "Serum...Albumin" = ALB) %>%
  st_units(units) %>%
  stable() %>% st_asis()
```



\clearpage

# Math

- Columns with at least two `$` are "math" and will not be sanitized
- Otherwise the are functions to "prime" the data frame
- The default is to convert every column to character
- Then walk the columns, look for non-math columns and sanitize them

```{r}
ptab <- readRDS("datasets/ptab.RDS")
ptab
```


```{r}
ptab %>% 
  st_data() %>% 
  st_center(Parameter = col_ragged(3), .l = "Symbol") %>%
  st_panel(".type") %>% 
  stable() %>% st_asis()
```



\clearpage

# hline from column

- Use the column to determine where the hline should go

```{r}
st_new(data) %>% 
  st_hline(from = "STUDY") %>% 
  stable() %>% st_asis()
```

\clearpage

# hline anywhere

- Give row numbers for hline

```{r}
st_new(data) %>% 
  st_hline(at = c(3,nrow(data))-1) %>%
  stable() %>% st_asis()
```

\clearpage

# hline pattern

```{r}
tmp <- readRDS("datasets/with-total.RDS")

st_new(tmp) %>% 
  st_hline(pattern = "all", cols = "STUDY", n = 2) %>% 
  stable() %>% st_asis()
```
\clearpage

# hline multiple

```{r}
tmp <- readRDS("datasets/with-total.RDS")

st_new(tmp) %>% 
  st_hline(at = 3, n = 2) %>% 
  stable() %>% st_asis()
```

\clearpage

# Mark a summary row (cf sumrows)

```{r}
tmp <- readRDS("datasets/with-total.RDS")

st_new(tmp) %>% 
  st_hline(at = 3, n = 2) %>% 
  st_bold(cols = "STUDY", pattern = "all") %>%
  st_edit(pattern = "all", replacement = "All studies") %>%
  stable() %>% st_asis()
```


\clearpage

# Remove duplicate values

- Discard repeating values in a column

```{r}
data %>% 
  st_new() %>% 
  st_hline(from = "STUDY") %>% 
  st_clear_reps("STUDY") %>% 
  stable() %>% st_asis()
```

\clearpage

# Add styling to data frame

- tex_bold will make table cells bold when they match `pattern`
- tex_it will make table cells italics when they match `pattern`
- styling is only added when there is at least one character
- input must be string
- combine this with `clear_rep` and `hline_from` to partition the table
```{r}
tmp <- ptdata() 
tmp <- mutate(tmp, STUDY = tex_bold(as.character(STUDY)))
```

```{r}
tmp %>% 
  st_new() %>% 
  st_clear_reps(STUDY) %>%
  st_hline(from = "STUDY") %>%
  stable() %>% st_asis()
```


\clearpage

# Add styling in the pipeline

```{r}
tmp <- ptdata()
```

```{r}

tmp %>%
  st_new() %>%
  st_clear_reps(STUDY, .now = TRUE) %>%
  st_hline(pattern = "\\S+", cols = "STUDY") %>%
  st_bold(cols = "STUDY") %>%
  st_it("DOSE") %>%
  st_edit("\\bmale", "dude") %>%
  st_edit("female", "gal") %>%
  stable() %>% st_asis()
```


\clearpage

# Panel

- Divide the table using column contents
- there's a bug somewhere there

```{r}

data %>% 
  st_new() %>% 
  st_center(DOSE = 'l', SCR = 'r') %>% 
  st_panel("STUDY", prefix = "Study number: ") %>% 
  stable() %>% st_asis()
```

\clearpage

# Colspan

- Group columns

```{r}
data %>% 
  st_new() %>% 
  st_left(.c = "WT,AGE,CRCL") %>% 
  st_span("In final model", WT:CRCL) %>% 
  stable() %>% st_asis()
```


\clearpage

# Colspan - multiple

- Multiple groupings
- Multiple levels

```{r}

data %>% 
  st_new() %>% 
  st_span("Meh", DOSE:WT) %>% 
  st_span("Hrm", AGE:CRCL) %>%
  st_span("Huh", ALB:SCR) %>% 
  st_span("Expert opinion", CRCL:SCR, level = 2) %>% 
  stable() %>% st_asis()
```


\clearpage

# Colspan - from cols

- we have some columns of the form `tag.name`

```{r}
dotdata <- readRDS("datasets/with-dots.RDS")
head(dotdata, n=2)
```

```{r}
dotdata %>% 
  st_new() %>%
  st_span_split(sep = '.') %>%
  stable() %>% st_asis()
```

\clearpage

# Handle wide columns

## `descr is` taking over the table
```{r}
ptable <- readRDS("datasets/ptable.RDS")

ptable %>% st_new() %>% stable() %>% st_asis()
```


## Limit `descr` to 5 cm

```{r}
ptable %>% 
  st_new() %>% 
  st_align(descr = col_ragged(5)) %>% 
  stable() %>% st_asis()
```


\clearpage

# Identify a summary row

We can point to one or more rows and style it up as a "summary row"

```{r}
df.total <- readRDS(file = "datasets/with-total.RDS")
df.total
```


```{r}
st_new(df.total) %>% 
  st_sumrow(pattern = "all", label = "All studies", bold = TRUE) %>% 
  stable() %>% st_asis()
```


\clearpage


# Fontsize

- Where's my glasses?

```{r}
data %>% st_new() %>% st_sizes(font = "tiny") %>% stable() %>% st_asis()
```


\clearpage

# Row space

```{r}
sl <- data %>% slice(1:3)
sl %>% st_new() %>%                         stable() %>% st_asis()
sl %>% st_new() %>% st_sizes(row = 0.9) %>% stable() %>% st_asis()
sl %>% st_new() %>% st_sizes(row = 2  ) %>% stable() %>% st_asis()
```
\clearpage

# Col space

```{r}
data %>% st_new() %>% st_sizes(col = 20) %>% stable() %>% st_asis()
```
